Verifying Demonstrations

### 2018-03-01 paper/BuildingBlocks.tex
Moves DB-anon-cred into building blocks
Updates anonymous credentials
coincoin

We need a few primitives with special properties to build our protocol.

\subsection{Collision-resistant hash functions}

@@

Thus we can instantiate \(\Hash\) with any algorithm from the SHA-2 or SHA-3 
families.

\input{DistanceBounding.tex}
\input{anon-cred.tex}
\input{LocationProofs.tex}
\input{TimeStamp.tex}

>>>>

In this section, we will briefly review the primitives that form the building blocks of \PRIVO.

%Seb: I am not sure that to explain hash functions as they are really basic primitives
\subsection{Collision-resistant hash functions}

@@

\(\Hash\) can be instantiated with any algorithm from the SHA-2 or SHA-3 families.

\input{ZKPK.tex}

\input{anon-cred.tex}

%\input{LocationProofs.tex}
%Seb: I have mode the location proofs to the

\input{DistanceBounding.tex}

\input{DB-anon-cred.tex}

\input{TimeStamp.tex}

### 2018-03-01 paper/DB-anon-cred.tex
coincoin

We pointed out in \cref{DistanceBounding} that the majority of all \ac{DB} 
protocols that provide the above security properties assume an \emph{honest} 
verifier.
This assumption does not hold in our setting, where every verifier at some point 
also might be a (malicious) prover.
We thus need public-key \ac{DB}, and more specifically \ac{DBPK}.

There is a protocol which provide \ac{DBPK} with all the desired properties from 
above, ProProx~\cite{ProProx}.
(Note that~\cite{ProProx} uses the abbreviation PoPoK, for Proof of Proximity of 
Knowledge.)
However, ProProx provides \iac{DBPK} protocol for quadratic residues, \ie for 
proving \(\DBPK[\alpha][a = \alpha^2]\).
We, on the other hand, need \iac{DBPK} protocol for discrete logarithms.
We will now introduce such a protocol which will allow us to do \ac{DB} 
anonymous credentials.
We note, however, that this protocol only provides \ac{DBMF}, \ac{DBDF}, 
\ac{DBDH} and \ac{DBIF} resistance --- \ie not \ac{DBTF} resistance.

@@

\emph{Reattempting \iacl{DB} Schnorr protocol.}
In the original \ac{DB} paper by \citet{DistanceBounding}, they proposed how to 
make the Schnorr identification scheme~\cite{Schnorr} distance bounding.
That \ac{DB} Schnorr protocol was shown to be prone to distance 
hijacking~\cite{DistanceHijacking}.
We now propose another way to turn the Schnorr protocol into \iac{DB} protocol 
which is secure against \ac{DBIV}, \ac{DBMF}, \ac{DBDF} and \ac{DBDH}.
It will not protect against terrorist fraud, although this would be desirable.

We present the protocol in \cref{SchnorrFigure}.
The difference from the original Schnorr protocol is that the prover commits to 
two random values and the verifier sends two challenges.
Then the verifier presents to the prover which commitment and challenge to use 
during the \ac{DB} phase.

@@

  \end{tabular}
  \caption{%
    One-round protocol instance of the \(\DBSprove\leftrightarrow \DBSverify\) 
    \ac{DB} Schnorr protocol for \(\PK[\alpha][A = g^\alpha]\).
    The protocol should be repeated in full to achieve the desired knowledge 
    error and distance-bounding error.
  }%
  \label{SchnorrFigure}
\end{figure*}

The intuition behind the protocol security is as follows.
To achieve malicious-verifier zero-knowledge we must choose \(k\) 
logarithmically in the security parameter \(\lambda\) and repeat the protocol 
until the knowledge error is small enough.
This will actually also decrease the success probability of \iac{DBMF} adversary 
in the \ac{DB} step.
The \ac{DBMF} adversary does not know which challenge the verifier will use, 
thus there is a \(1/2\) probability that the \ac{DBMF} adversary will guess it 
correctly.
The prover will only provide one of the responses: even if the adversary re-runs 
the protocol with the same challenges, the randomly chosen \(\rho_0, \rho_1\) 
will have changed --- which thus yields another \(R_b\) in the end of the 
protocol.
By repeating the protocol we decrease this probability.

@@

The \ac{DB} phase also ensures that \iac{DBMF} adversary will fail the \ac{DB} 
phase for at least one round.
The verifier will send \(\ceil{\log_2 q} + l < 2\ceil{\log_2 q}\) challenges.
Thus the prover reveals all the bits of either \(s_0\) or \(s_1\) but only \(l\) 
bits of the other.
Thus, the adversary can buffer \(l\) bits of both \(s_0, s_1\) by requesting 
them from the prover.
But at this point the adversary must wait for \(b_{l+1}\) from the verifier and 
then relay that challenge to the prover to receive the correct \(r_i\) --- this 
relay will be detected.

The protocol is also secure against distance hijacking.
This follows from the fact that it is the authenticating bit string that is used 
during the \ac{DB} phase.

>>>>

We pointed out in \cref{DistanceBounding} that the majority of all \ac{DB} protocols that provide the above security properties assume an \emph{honest} verifier.
This assumption does not hold in our setting, in which every verifier might also be at some point a (malicious) prover.
We thus need public-key \ac{DB}, and more specifically \ac{DBPK}.

There is a protocol which provide \ac{DBPK} with all the desired properties from above, ProProx~\cite{ProProx}.
(Note that~\cite{ProProx} uses the abbreviation PoPoK, for Proof of Proximity of Knowledge.)
However, ProProx provides \iac{DBPK} protocol only for quadratic residues (\ie for proving \(\DBPK[\alpha][a = \alpha^2]\)) while in our context, we need a \iac{DBPK} protocol for discrete logarithms.
To realize this, we will now introduce such a protocol that will allow us to do \ac{DB} anonymous credentials.
We note, however, that this protocol only provides \ac{DBMF}, \ac{DBDF}, \ac{DBDH} and \ac{DBIF} resistance --- but not \ac{DBTF} resistance.

@@

\emph{New attempt of \iacl{DB} Schnorr protocol.} In the original \ac{DB} paper by \citet{DistanceBounding}, they show how to design a distance bounding protocol based on the Schnorr identification scheme~\cite{Schnorr}.
That \ac{DB} Schnorr protocol was shown to be prone to distance 
hijacking~\cite{DistanceHijacking}.
We now propose another way to turn the Schnorr protocol into \iac{DB} protocol 
which is secure against \ac{DBIV}, \ac{DBMF}, \ac{DBDF} and \ac{DBDH}.
It will not protect against terrorist fraud, although ideally this property should be desirable.

We present the protocol in \cref{SchnorrFigure}.
The difference from the original Schnorr protocol is that the prover commits to two random values and the verifier sends two challenges.
Afterwards, the verifier presents to the prover which commitment and challenge to use during the \ac{DB} phase.

@@

  \end{tabular}
  \caption{%
    One-round protocol instance of the \(\DBSprove\leftrightarrow \DBSverify\) \ac{DB} Schnorr protocol for \(\PK[\alpha][A = g^\alpha]\).
    The protocol should be repeated in full to achieve the desired knowledge and distance-bounding errors.
  }%
  \label{SchnorrFigure}
\end{figure*}

The intuition behind the protocol security is as follows.
To achieve malicious-verifier zero-knowledge we must choose \(k\) logarithmically in the security parameter \(\lambda\) and repeat the protocol until the knowledge error is small enough.
This will actually also decrease the success probability of \iac{DBMF} adversary in the \ac{DB} step.
Indeed, the \ac{DBMF} adversary does not know which challenge the verifier will use, thus there is a \(1/2\) probability that the \ac{DBMF} adversary will guess it correctly.
The prover will only provide one of the responses: even if the adversary re-runs the protocol with the same challenges, the randomly chosen \(\rho_0, \rho_1\) will have changed --- which thus yields another \(R_b\) in the end of the protocol.
A sequential repetition of protocol will decrease this probability.

@@

The \ac{DB} phase also ensures that \iac{DBMF} adversary will fail the \ac{DB} phase for at least one round.
The verifier will send \(\ceil{\log_2 q} + l < 2\ceil{\log_2 q}\) challenges.
Thus the prover reveals all the bits of either \(s_0\) or \(s_1\) but only \(l\) bits of the other.
Thus, the adversary can buffer \(l\) bits of both \(s_0, s_1\) by requesting them from the prover.
However at this point the adversary must wait for \(b_{l+1}\) from the verifier and then relay that challenge to the prover to receive the correct \(r_i\) --- this relay will be detected.

The protocol is also secure against distance hijacking due to the fact that it is the authenticating bit string that is used 
during the \ac{DB} phase.

### 2018-03-01 paper/DistanceBounding.tex
change to intro and system model
Changes "i.e.\ " and "e.g.\ " to \ie and \eg
coincoin

% XXX Better intro to distance bounding
\Ac{DB} protocols were first suggested by \citet{DistanceBounding}.
Over the years the desirable properties of \ac{DB} protocols can be summarized 
as follows:
\begin{itemize}
    % XXX Describe the DB frauds in more detail, i.e. explain them.
  \item \ac{DBMF} resistance,
  \item \ac{DBDF} resistance,
  \item \ac{DBDH} resistance,
  \item \ac{DBTF} resistance,
  \item \ac{DBIF} resistance,
\end{itemize}
There are two lines of attempts at formalizing the above properties: one by 
\citet{DB-BMV} and another by \citet{DB-DFKO}.

The majority of the existing \ac{DB} protocols are symmetric and thus requires 
an honest verifier.
There has been less work done in the domain of asymmetric (or public-key) 
\ac{DB} protocols.
Unfortunately, our setting requires a public-key \ac{DB} protocol with a 
\emph{malicious verifier} who will try to \emph{impersonate the prover}.
The verifier might also try to track the provers and map their identities to 
their actions, thus we also require privacy.
This leads to the requirement of a \ac{DB} \ac{ZKPK}, or simply \ac{DBPK}, with 
resistance to all the frauds mentioned above as well as against this verifier 
who will attempt to impersonate the prover.
More specifically, we must combine such \iac{DB} with anonymous credentials, 
which we will describe next.

>>>>

\Ac{DB} protocols were first suggested by \citet{DistanceBounding} to prevent relay attacks contactless communications in which the adversary forwards a communication between a prover and a possibility far-away verifier to authenticate. 
These attacks cannot be prevented by cryptographic tools as they are independent of the semantics of the messages exchanged and mechanisms ensuring the physical proximity between a verifier and a prover must be used.
\Ac{DB} protocols precisely enable the verifier to estimate an upper bound on his distance to the prover by measuring the time-of-flight of short challenge-response messages (or rounds) exchanged during time-critical phases. 
Time critical phases are complemented by slow phases during which the time is not taking into account.
At the end of a \Ac{DB} protocol, the verifier should be able to determine if the prover is legitimate and in his vicinity.

The main security requirements of \ac{DB} protocols can be summarized as follows:
\begin{itemize}
    % XXX Describe the DB frauds in more detail, i.e. explain them.
  \item \ac{DBMF}: the adversary illegitimately authenticates, possibly using a far-away honest prover.
  \item\ac{DBTF}: a malicious prover helps an accomplice to authenticate.
    \item \ac{DBDF}: a legitimate but malicious prover wants to fool the verifier on the distance between them.
  \item \ac{DBDH}: similar to \ac{DBDF}, sometimes using the presence of an honest prover close to the verifier.
  \item \ac{DBIF}: the adversary plays against a simplified version of the protocol without any distance estimation.
\end{itemize}
There are two lines of attempts at formalizing the above properties: one by \citet{DB-BMV} and another by \citet{DB-DFKO}.

The majority of the existing \ac{DB} protocols are symmetric and thus requires an honest verifier.
Indeed, in this context it does not make sense to protect against the verifier as he can impersonate easily the prover as he has a knowledge of his secret key.
There has been less work done in the domain of asymmetric (or public-key) \ac{DB} protocols.
Unfortunately, our setting requires a public-key \ac{DB} protocol with a \emph{malicious verifier} who will try to \emph{impersonate the prover}.
The verifier might also try to track the provers and map their identities to their actions, thus we also require privacy.
This leads to the requirement of a \ac{DB} \ac{ZKPK}, or simply \ac{DBPK}, with resistance to all the frauds mentioned above as well as against this verifier 
who will attempt to impersonate the prover.
More specifically, we must combine such \iac{DB} with anonymous credentials, which we will describe next.
The anonymous credential system will affect what properties we require of the \ac{DBPK}, (\eg that it must be \iac{PKE} for discrete logarithms).
%Seb: I have created the acronym DBPK in bibsp.sty

### 2018-03-01 paper/properties.tex
coincoin

We note that we cannot actually improve the privacy of participating protesters during the protest: if Alice is caught during a protest or other crowd-counting mechanisms based on photographic or video evidence are used to identify Alice, there is nothing we can do. 
%Seb: suggestion maybe we should put the following part in the discussion
However, in \PRIVO, we aim at verifiable participation count that does not add any threats to the participants' privacy. 
For instance, if there are counter-protests in the \emph{same location at the same time}, Alice could even blend into another crowd and argue that she participated in a different protest than she actually did --- and the counts would still be correct afterwards.
However, even if there is only one protest and she is not caught in the act, then using our proposed mechanism should not incur any additional risk.
Thus we need at least participation-proof privacy but receipt freeness is also desired.
In essence, this means that upon completing the protocol, Grace cannot link Alice to Alice's participation proof --- even if she were to compromise Alice's device.
%Sonja says: I'm confused: can we or can we not provide this?
%Seb: I agree with Sonja, it is not clear whether we achieve it or not

>>>>

We note that we cannot actually improve the privacy of participating protesters during the protest: if Alice is caught during a protest or other crowd-counting mechanisms based on photographic or video evidence are used to identify Alice, there is nothing we can do. 
%Seb: suggestion maybe we should put the following part in the discussion
However, in \PRIVO, we aim at verifiable participation count that does not add any threats to the participants' privacy. 
For instance, if there are counter-protests in the \emph{same location at the same time}, Alice could even blend into another crowd and argue that she participated in a different protest than she actually did --- and the counts would still be correct afterwards.
However, even if there is only one protest and she is not caught in the act, then using our proposed mechanism should not incur any additional risk.
Thus we need at least participation-proof privacy but receipt freeness is also desired.
In essence, this means that upon completing the protocol, Eve cannot link Alice to Alice's participation proof --- even if she were to compromise Alice's device.
%Sonja says: I'm confused: can we or can we not provide this?
%Seb: I agree with Sonja, it is not clear whether we achieve it or not
